Small(er) Samples

### 2022-01-12 R/smaller_samples.Rmd
Change data source, fix plots

options(digits = 3)
options(scipen = 4)

df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)
df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521",
         !is.na(mass))
```

@@

```{r}
df %>% 
ggplot(aes(mass, c12ua, color = Name)) +
  geom_point() +
  ggtitle()
```

@@

```{r}
df %>% 
ggplot(aes(c12ua, abs(fm_diff))) +
  geom_smooth() +
  geom_point(aes(color = wheel))
```

```{r}
df %>% 
  filter(sample_type == "S") %>% 
ggplot(aes(c12ua, abs(fm_diff))) +
  geom_point(aes(color = wheel))
```

>>>>

options(digits = 3)
options(scipen = 4)
```

```{r}
# Read reduced data as produced by analyse_carbonates.R
df <- readRDS(here("data_analysed/carb_all.rds")) %>% 
  map_dfr(2) %>% 
#df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)
df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521")
```

@@

```{r}
df %>% 
ggplot(aes(mass, c12ua, color = Name)) +
  geom_point()
```

@@

```{r}
df %>% 
ggplot(aes(c12ua, abs(fm_diff))) +
  geom_smooth(method = "lm") +
  geom_point(aes(color = wheel))
```

```{r}
df %>% 
  filter(sample_type == "S") %>% 
ggplot(aes(c12ua, abs(fm_diff))) +
  geom_smooth(method = "lm") +
  geom_point(aes(color = wheel))
```
